---
title: "Unsupervised Aggregattion of Rows in Large Dataframe"
author: "Maximilian Nölscher"
date: "10 März 2020"
output: rmarkdown::github_document
---

```{r, include=FALSE}
purrr::map(
  list.files(
    path = './functions',
    pattern = "\\.R$",
    full.names = TRUE,
    recursive = TRUE
  ),
  source
)
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.align = "center")

opts <- options(knitr.kable.NA = "")
```

# Libraries
```{r}
library(tidyverse)
```


# Data Import

```{r}
data_dummy <- read_csv2('raw_data/data_dummy.csv')
```

Clean the column names
```{r}
data_dummy <- data_dummy %>% 
  janitor::clean_names() %>% 
  mutate(date = lubridate::dmy(date)) %>% 
  mutate_at(c('column_b', 'column_c', 'column_d'), as.numeric)
```


Show the dataframe
```{r, out.width='100%'}
data_dummy %>% 
  knitr::kable("markdown")
```


# Problem Definition
The goal is to merge duplicates of rows. The criterion for duplicates is 

* same `proj_id` value
* same `date` value

## Find Duplicates

### Way 1 - Janitor
```{r}
data_dummy_duplicates <- data_dummy %>% 
  janitor::get_dupes(proj_id, date) %>% 
  select(-dupe_count)
```

Show the resulting dataframe
```{r}
data_dummy_duplicates %>% 
  knitr::kable("markdown")
```

```{r, include = FALSE}
# Alternitavely
data_dummy %>% 
  group_by(proj_id, date) %>% 
  filter(n() > 1) %>% 
  arrange(proj_id)
```

# Aggregation

## Method 1 - with prioritizing confidence

### `priority_key`

In the following steps we define a dataframe containing priorities to each unique project
```{r}
priority_key <- data_dummy %>% 
  distinct(proj)
```

Now we add values for the priorities
```{r}
priority_key <- priority_key %>% 
  mutate(priority = c(5, 3, 1, 2, 4))
```

Show the resulting dataframe
```{r}
priority_key %>% 
  knitr::kable("markdown")
```

We join the 2 dataframes
```{r}
data_dummy <- data_dummy %>% 
  left_join(priority_key, by = 'proj')
```

Show the resulting dataframe
```{r}
data_dummy %>% 
  knitr::kable("markdown")
```

### Aggregating the `data_dummy` dataframe

1. We group the dataframe depending on our duplicate criteria `proj_id` and `date`
2. we sort them by priority
3. and simply chose the first non `NA` value in each group
4. remove the column `priority`
```{r}
data_dummy_aggregated <- data_dummy %>% 
  group_by(proj_id, date) %>% 
  arrange(priority) %>% 
  summarise_all(funs(first(na.omit(.)))) %>% 
  select(-priority)
```

This results in an aggregated dataframe, where cell values are chosen

1. by prioritizing the source
2. fill in the only availyble value in a column

Show the resulting dataframe. For comparison the dateframe containing the duplicates is displayed below.
```{r}
data_dummy_aggregated %>% 
  list(., data_dummy_duplicates) %>% 
  knitr::kable("markdown") %>% 
  kableExtra::kable_styling(full_width = TRUE)
```

